A Fast Unified Model for Parsing and Sentence Understanding

### 2016-03-18 writing/hard_stack_paper/paper.tex
Proofreading the rest of the paper.

To classify an SNLI sentence pair, we run two copies of SPINN with shared parameters: one on the premise sentence and another the hypothesis sentence. We then use their outputs (the $\vec{h}$ states at the top of each stack at time $t=T$) to construct a feature vector $\vec{x}_{\text{classifier}}$ for the pair. This feature vector consists of the concatenation of these two sentence vectors, their difference, and their elementwise product:
\begin{equation}
\vec{x}_{\text{classifier}} = 
\colvec{4}
    {\vec{h}_{\text{premise}}}
    {\vec{h}_{\text{hypothesis}}}
    {\vec{h}_{\text{premise}} - \vec{h}_{\text{hypothesis}}}
    {\vec{h}_{\text{premise}} \odot \vec{h}_{\text{hypothesis}}}
\end{equation}
Following \citet{snli:emnlp2015}, this feature vector is then passed to a series of ReLU neural network layers (i.e., an MLP; the number of layers is tuned as a hyperparameter), then passed into a linear transformation, and then finally passed to a softmax layer, which yields a distribution among the three labels.

@@

We train each model for 250k steps in each run, using a batch size of 32. We track each model's performance on the development set during training and save parameters when this performance reached a new peak. We use early stopping, evaluating on the test set using the parameters that perform best on the development set.

@@

Both SPINN-PI and the full SPINN outperform all previous sentence encoding models by a significant margin. Most notably our models outperform the Tree-based CNN of \citet{mou2015recognizing}, which also uses tree-structured composition for local feature extraction, but uses simpler pooling techniques to build sentence features in the interest of efficiency. Our results show that a model that uses tree-structured composition fully (SPINN) outperforms one which uses it only partially (Tree-based CNN), which in turn outperforms one which does not use it at all (LSTM RNN).

@@

We suspect that the hybrid nature of the full SPINN model is also responsible for its ability to perform better than an RNN baseline even when its internal parser is relatively ineffective at producing correct full-sentence parses. We suspect that it is acting somewhat like the Tree-based CNN, only with access to larger trees: Using tree structure to build up local phrase meanings, and then using the tracking LSTM, at least in part, to combine those meanings.

>>>>

To classify an SNLI sentence pair, we run two copies of SPINN with shared parameters: one on the premise sentence and another the hypothesis sentence. We then use their outputs (the $\vec{h}$ states at the top of each stack at time $t=T$) to construct a feature vector $\vec{x}_{\text{classifier}}$ for the pair. This feature vector consists of the concatenation of these two sentence vectors, their difference, and their elementwise product:
\begin{equation}
\vec{x}_{\text{classifier}} = 
\colvec{4}
    {\vec{h}_{\text{premise}}}
    {\vec{h}_{\text{hypothesis}}}
    {\vec{h}_{\text{premise}} - \vec{h}_{\text{hypothesis}}}
    {\vec{h}_{\text{premise}} \odot \vec{h}_{\text{hypothesis}}}
\end{equation}
Following \citet{snli:emnlp2015}, this feature vector is then passed to a series of ReLU neural network layers (i.e., an MLP; the number of layers is tuned as a hyperparameter), then passed into a linear transformation, and then finally passed to a softmax layer, which yields a distribution over the three labels.

@@

We train each model for 250k steps in each run, using a batch size of 32. We track each model's performance on the development set during training and save parameters when this performance reaches a new peak. We use early stopping, evaluating on the test set using the parameters that perform best on the development set.

@@

Both SPINN-PI and the full SPINN outperform all previous sentence encoding models by a significant margin. Most notably our models outperform the Tree-Based CNN of \citet{mou2015recognizing}, which also uses tree-structured composition for local feature extraction, but uses simpler pooling techniques to build sentence features in the interest of efficiency. Our results show that a model that uses tree-structured composition fully (SPINN) outperforms one which uses it only partially (Tree-Based CNN), which in turn outperforms one which does not use it at all (LSTM RNN).

@@

We suspect that the hybrid nature of the full SPINN model is also responsible for its ability to perform better than an RNN baseline even when its internal parser is relatively ineffective at producing correct full-sentence parses. We suspect that it is acting somewhat like the Tree-Based CNN, only with access to larger trees: Using tree structure to build up local phrase meanings, and then using the tracking LSTM, at least in part, to combine those meanings.
